%-------------------------
% Resume in LaTeX
% Author: Sagar Thapa Chhetri
%-------------------------

\documentclass[a4paper,11pt]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{helvet}

% Use Helvetica as default font
\renewcommand{\familydefault}{\sfdefault}

% Page geometry
\geometry{
    left=0.75in,
    right=0.75in,
    top=0.6in,
    bottom=0.6in
}

% Colors (matching the resume)
\definecolor{primaryteal}{HTML}{006666}
\definecolor{linkcolor}{HTML}{0A9FB5}
\definecolor{headingcolor}{HTML}{333333}
\definecolor{datecolor}{HTML}{333333}
\definecolor{backgroundcream}{HTML}{FFFDE7}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor,
    pdfborder={0 0 0}
}

% Section formatting with teal line
\titleformat{\section}{
    \Large\bfseries\color{headingcolor}
}{}{0em}{}[\color{primaryteal}\titlerule]

\titlespacing*{\section}{0pt}{10pt}{6pt}

% Subsection formatting
\titleformat{\subsection}{
    \large\bfseries\color{black}
}{}{0em}{}

\titlespacing*{\subsection}{0pt}{8pt}{4pt}

% Remove page numbers
\pagenumbering{gobble}

% Custom commands
\newcommand{\resumeSubheading}[4]{
    \noindent
    \begin{tabularx}{\textwidth}{Xr}
        \textbf{#1} & \textcolor{datecolor}{\textbf{#2}} \\
        \textit{#3} & \textit{#4}
    \end{tabularx}
    \vspace{2pt}
}

\newcommand{\resumeItem}[1]{
    \item #1
}

\newcommand{\projectHeading}[2]{
    \noindent\textbf{#1} \href{#2}{\textcolor{linkcolor}{[LINK]}}
}

\newcommand{\projectHeadingNoLink}[1]{
    \noindent\textbf{#1}
}

%-------------------------
% DOCUMENT START
%-------------------------
\begin{document}

%-------------------------
% HEADER
%-------------------------
\begin{tabularx}{\textwidth}{Xr}
    \begin{minipage}[t]{0.65\textwidth}
        {\fontsize{28}{32}\selectfont\bfseries\color{headingcolor} Sagar Thapa Chhetri}\\[2pt]
        {\large\bfseries\color{headingcolor}FullStack Developer}
    \end{minipage}
    &
    \begin{minipage}[t]{0.3\textwidth}
        \raggedleft\small
        +9779869477113\\
        reyzon.thapa2020@gmail.com\\
        {\color{primaryteal}\underline{\href{https://portfolio.com}{Portfolio Website}}} {\color{primaryteal}\underline{\href{https://linkedin.com}{LinkedIn}}} {\color{primaryteal}\underline{\href{https://github.com}{Github}}}
    \end{minipage}
\end{tabularx}

\vspace{10pt}

%-------------------------
% WORK EXPERIENCE
%-------------------------
\section{Work Experience}

\noindent
\begin{tabularx}{\textwidth}{Xr}
    {\bfseries\color{headingcolor}FullStack Developer at Bootwall R\&D} & {\bfseries\color{datecolor}Feb 2023-Jan 2024}
\end{tabularx}

\noindent
I worked as a MERN stack developer in Bootwall R\&D. During my tenure I was involved in the projects like College MS, Gym MS, Ecommerce Apps and Blockchain based Defi apps.

\vspace{12pt}

\noindent
\begin{tabularx}{\textwidth}{Xr}
    {\bfseries\color{headingcolor}Full Stack Developer at Beyond Labs} & {\bfseries\color{datecolor}March 2024-present}
\end{tabularx}

\vspace{6pt}

{\bfseries\color{headingcolor}Monorepo Architecture}
\begin{itemize}[leftmargin=20pt, itemsep=2pt, topsep=2pt]
    \item Worked on a unified monorepo containing BeyondAI Docs, shared APIs, and frontend applications
    \item Developed frontend using Next.js and backend APIs with Fastify.
    \item Utilized PostgreSQL for data storage and Redis for caching and session management.
\end{itemize}

{\bfseries\color{headingcolor}Serverless Architecture using Lambda \& Defi Copilot on NextJS}
\begin{itemize}[leftmargin=20pt, itemsep=2pt, topsep=2pt]
    \item Worked on a TDD environment against DB with multiple services like authentication, wallet \& telegram.
    \item Involved on building Defi copilot using llms like openai, grok-3 using light ruled based instruction.
    \item Handled db migration from Postgres to DynamoDB using script and batching techniques.
\end{itemize}

%-------------------------
% TECH SKILLS
%-------------------------
\section{Tech Skills}

\begin{tabularx}{\textwidth}{XX}
    {\bfseries\color{headingcolor}Front End} & {\bfseries\color{headingcolor}Backend} \\
    \small React, Redux, Typescript, HTML5, CSS3 & \small Node JS, Restful APIs, Serverless lambda, \\
    \small TanStack, UI Libraries & \small Postgres, MongoDB \\[8pt]
    {\bfseries\color{headingcolor}Devops} & {\bfseries\color{headingcolor}Other Skills} \\
    \small Basics of Docker \& Soft TDD using CI & \small Git/Github, Trello, Slack \\
    \small Vercel \& Netlify for deployment & \\
\end{tabularx}

%-------------------------
% PROJECTS
%-------------------------
\section{Projects}

{\bfseries\color{headingcolor}Defi Copilot Agent based on Hedera chain} {\color{primaryteal}\underline{\href{https://example.com}{[LINK]}}}\\
\small AI-powered DeFi Copilot on Hedera that lets anyone instantly create tokens, view balances, add liquidity, and perform swaps through a single automated interface. It removes all the technical complexity of smart contracts, approvals, ratios, and routing, turning advanced DeFi actions into simple, one-step commands for users of any skill level.

\vspace{8pt}

{\bfseries\color{headingcolor}Food Ordering System}\\
\small A web based Food ordering system, where user can place an order and pay through web3 wallet. The system also involves the meal management, order processings.

\vspace{8pt}

{\bfseries\color{headingcolor}Trade Flux (DEX)} {\color{primaryteal}\underline{\href{https://example.com}{[LINK]}}}\\
\small It is an DeFi app where user can set an order based on BTC as a trigger price. User can place a limit order based on the price action of BTC or ETH. It is because the price of BTC is crucial for other ALT tokens. Eg when BTC drops 10\%, most of the ALTs drops by 25-30\% so this system provides us an advantage of buying Alts when BTC drops \& vice versa.

\vspace{8pt}

{\bfseries\color{headingcolor}Petgomania (Pet Commerce \& Adoption)}\\
\small This is a ecommerce website for pet shops where the shop owner can list their products, execute orders, manage inventories. It also has a feature for pet adoption (Cats \& Dogs). It has a chat feature so that user can interact with the pet owner for queries.

\end{document}
